Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment

### 2018-01-13 paperDraft3.tex
latest verstion

\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, fullpage}
\usepackage{array}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

@@

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

@@

\author{Kassandra M.\ Fronczyk\\Lawrence Livermore National Laboratory\\Livermore, CA\\\texttt{fronczyk1@llnl.gov} \and
Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu} \and
James F.\ Gilman\\North Carolina State University\\Raleigh, NC\\\texttt{jfgilman@ncsu.edu}
}
\maketitle} \fi

@@

\begin{abstract}
    We use a Bayesian hierarchical model to assess the reliability of the Joint
    Light Tactical Vehicle (JLTV), which is a family of vehicles. The proposed
    model effectively combines information across three phases of testing and
    across common vehicle components. The analysis yields estimates of failure
    rates for specific failure modes and vehicles as well as an overall estimate
    of the failure rate for the family of vehicles. We are also able to obtain
    estimates of how well vehicle modifications between test phases improve
    failure rates. In addition to using all data to improve on current
    assessments of reliability and reliability growth, we illustrate how to
    leverage the information learned from the three phases to determine
    appropriate specifications for subsequent testing that will demonstrate if
    the reliability meets a given reliability threshold.
\end{abstract}

@@

\newpage

\section{Introduction}
Reliability is a high priority in the testing of military systems. A common
interest is {\em reliability growth}, which tracks the change, and ideally
improvement, in the reliability of a system as it moves through testing phases
and undergoes periodic corrective actions. Ideally, plans for future test events
should be based on what is observed in previous testing.

In this paper, we look at combining information across multiple test phases with
the objective of planning a future test. When combining information, there is no
omnibus solution. Rather, models need to be carefully considered and evaluated
to ensure that they accurately reflect the data and the underlying physical
processes. Our analysis is motivated by reliability data from the Joint Light
Tactical Vehicle (JLTV), which is a family of vehicles designed to replace
one-third of the legacy high-mobility multipurpose wheeled vehicle (Humvee)
fleet. There are four unique types of vehicles, and within types there are many
possible variants. The primary mission of the family of vehicles is to provide
ground mobility that is deployable worldwide and capable of operating across the
range of military roles including combat, sustainment, police action,
peacekeeping, and security patrol, in all weather and terrain conditions.

The JLTV has been through a series of test events as it has been developed.
Engineering and Manufacturing Development (EMD) included three phases of
testing, where fixes occurred only during a set Corrective Action Period (CAP)
between each phase. For every vehicle, each failure encountered during testing
was recorded and attributed to a specific failure mode.  Since fixes were
delayed to CAPs, analysis generally shows a distinct jump in the system
reliability between test phases.

@@

\section{Data}
Eight vehicle prototypes were used for reliability, availability,
and maintainability (RAM) testing. There were four two-seat utility vehicles,
two four-seat general purpose vehicles, a two-seat heavy guns carrier, and a
two-seat close combat weapons carrier. The close combat weapons carrier, one
general purpose, and two utility vehicles were tested in Aberdeen, Maryland,
where it is much colder in the winter months but the terrain is not as harsh,
and the heavy weapons carrier, one general purpose, and two utility vehicles
were tested in Yuma, Arizona, where it is warmer but with more challenging
terrain, to attain testing in different environmental and terrain conditions.
The vehicles were driven roughly 3000 to about 5000 miles in Phase 1, between
4500 and 7500 miles in Phase 2, and between 5000 and 6700 miles in Phase
3.\footnote{The exact mileage has been altered to protect proprietary
information.}

There are many similarities between vehicle types; in fact, the most dissimilar
vehicles have over 80\% common parts. Consequently, some failure modes, such as
brakes and radios, will be common to all eight vehicles. Other failure modes
will be related, but not identical, as with hydraulics, frame, and body.

There are 1412 observed failures attributed to 26 failure modes recorded across
all eight vehicles and all three test phases. In any given phase of test, every
vehicle is not guaranteed to have a failure of all 26 failure modes, and each
test phase does not necessarily end with a failure. Therefore, we have 624 right
censored observations, accounting for miles driven without observed failures.

\section{Methodology}

\subsection{Modeling Reliability}
A standard reliability analysis employed by the Department of Defense (DoD) test
community considers each test phase independently and uses the exponential
distribution to model the miles between failure for the system ~\cite{ref1}. The
traditional analysis is overly simplistic, relies on correct modeling
assumptions and ignores valuable information learned about the individual
vehicles and their failure modes.

In this paper, we propose an alternative approach using a Bayesian hierarchical
model.  The methodology section is organized as follows.  In section 3.1 we
begin by introducing a general structure that models the relationships in the
data across all test phases while accounting for CAPs and incorporates known
similarities between vehicle failure modes.  Next, we will consider different
distributional assumptions and their implications.  Using the JLTV case study we
will illustrate the process of model selection using three different diagnostic
checks.  In section 3.2 we discuss methods of designing next stage test plans.
First we outline the traditional approaches, then we walk through a Bayesian
approach that allows the practitioner to incorporating the models developed from
section 3.1 with the hopes of reducing testing resources required while still
minimizing producer and consumer risks.

In this reliability setting we are analyzing time of failure data measured in
miles for a multiple component system with the primary objective being
assessment of the system failure rate and prediction of future failure counts.
The most common models used in this failure rate analysis are lifetime
distributions and the most common for failure count analysis is the
\emph{Poisson process} family of counting model.  We will utilize both and
specifically the relationships between them in planning future test.

\subsubsection{Model Structure}
Introducing notation, for each phase of testing we have failure mileage data for
a given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the censored
observation at the end the testing phase. In each phase of testing, we assume
the vehicle miles between failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a
lifetime distribution $f(\cdot)$, with an unknown set of parameters that include
a rate parameter.  For the first phase the rate parameter for vehicle $i$ and
failure mode $j$ will be denoted as $\lambda_{ij}$.  Then for the next stage we
will use the same $\lambda_{ij}$ but add a multiplicative correction parameter
$\rho_{j}^{P2}$ that represents the change in this rate due to the CAP.  This
procedure is then repeated for each subsequent stage.  The correction parameter
will be discussed more in the next section but the general model is as follows,
\begin{align*}
\text{Phase 1: }&y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
j=1,2,...,s \quad k=1,2,...,n_{ij}\\
\text{Phase 2: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\sim f(\cdot) \\
\text{Phase 3: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\rho_{j}^{P3}\sim f(\cdot)
\end{align*}
where $v$ represents the number of vehicles, $s$ is the number of failure modes,
and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$.

% The number of failure modes is assumed fixed and known \textit{a priori}.

For the model we assume a prior distribution on failure rate parameter
$\lambda_{ij}$.  This distribution depends on whether failure mode $j$ is
considered to be common across vehicles or related but not identical.  If
failure mode $j$ is considered common across vehicles we will assume there is a
single failure rate $\lambda_j$ that is shared by all eight vehicles with a
prior distribution that has positive support.  In the JLTV study we will use a
non-informative gamma distribution.  For failure modes that are considered
related across vehicles but not expected to be exactly the same, we place a
prior distribution on the collection of $\lambda_{ij}$; in other words, we
assume each of the vehicles has a distinct failure rate for failure mode $j$ but
they arise from a common distribution.  This is the common Bayesian hierarchical
modeling structure, where we then place  hyperprior distributions on the shared
distribution's parameters.  In the JLTV study we use a gamma distribution with
non-informative hyperpriors for all related failure modes.  Many times in
practice  it is difficult to know ahead of time if individual components should
be modeled  as common or related.  In the JLTV study we fit models for each
component with both model structures and used diagnostic tools  that are
discussed in a later section to make our final decision.

\subsubsection{Fix Effectiveness}
After the first CAP, Test Phase 2 begins with the repaired vehicles. To capture
these revisions, the PM2 reliability growth model \cite{ref2} is often used.
This model explicitly captures testing phases, choices about which failure modes
to correct, and the potential of not completely eliminating a failure upon
repair. One of the downsides of PM2 is that many parameters of potential
interest, such as the Fix Effectiveness Factor (FEF), which measures how much
repairs improve failure rates, are typically fixed. A common value for FEF is
0.70. We follow the premise of this type of model, but allow a more flexible and
data-driven result that is less dependent on hard-coded assumptions.

One normal assumption used in reliability growth modeling is nondecreasing
failure rates; that is either the fixes were effective or had no effect, but did
not degrade the family of vehicles.  This should generally be the case, but
because we are dealing with complex systems and testing conditions are rarely
completely consistent, we will sometimes see decreases in failure rates after
adjustments are made.  Thus we will choose a prior distribution for the
correction parameter $\rho_{j}^{P2}$ that has positive support.  If
$\rho_{j}^{P2}$ is less than one, this represents an improvement in reliability.
And the same thinking is applied to $\rho_{j}^{P3}$ for the correction period
between phases two and three.  With this structure we can use the posterior
distributions of the correction parameters to make inference on the effectiveness
of the repairs and the join posterior distributions to evaluate the overall
system reliability within each phase.

\subsubsection{Distributional Assumption}
The next modeling choice that must be made is selecting an appropriate
probability model This includes a selecting a sampling distribution for the data
and prior distributions for each parameter on which the sampling distribution
depends.  For lifetime data there are a number sampling distribution to choose
from.  Some common choices are exponential, Weibull, lognormal, gamma, inverse
Gaussian, and normal failure time models.  Because all of these distributions
have rate parameter (sometimes called scale = 1/rate) they can be applied to
the proposed modeling structure.  For this paper, we will focus on the
exponential and Weibull distributions.

First the exponential model,
\begin{equation*}
    f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}y_{ijk})
\end{equation*}

This is by far the most common parametric distribution used in reliability
modeling because of its desirable math mathematical properties and simple
interpretations.  One of the convenient properties, because we are assuming
independence between failure modes, is the overall system failures also follow
an exponential distribution with a system failure rate $\lambda_S =
\sum_{j}\lambda_{j}$.  A second, possibly less attractive property, is that the
hazard rate is constant over miles.  For the JLTV, setting this would assume that a given
component is equally likely to fail in the first mile of testing as it is in the
thousandth.  This may be reasonable for some reliability settings, but in most
setting we observe either a decreasing hazard rate where failures are likely to
occur early in testing but less likely as the test goes on, or increasing hazard
rate where we see the system wear down as the test progresses.

Despite its common uses the assumption of a constant hazard rate over time is
rarely justifiable.  It has been well documented the issues that can arise when
this assumption is violated ~\cite{ref3}.  Therefore we will also consider more
flexible distributions when analyzing the data.  In our analysis of the JLTV
data we fit the same hierarchical model structure using the Weibull as our
lifetime distribution $f(\cdot)$.  Now we assume that the failure mileage
$t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$ distribution with scale
parameter $\lambda$ and shape parameter $\gamma$, with probability density
function,
\begin{equation*}
    f(t_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
    t_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} t_{ijk}^{\gamma_{i}}).
\end{equation*}
The exponential is a special case of the Weibull, when $\gamma = 1$.  You should
notice here we are now modeling the actual failure mileage $t_{ijk}$ instead of
the miles between failures $y_{ijk}$.  This implies the "bad as old" assumption
for intra-test repairs.  We could have continued with the miles between failures
and assumed "good as new" repairs, but "bad as old" modeling will be more
convenient for developing assurance test plans in later sections.  This
distinction is important in the Weibull case because the failure rate is not
constant in time. In practice the decision on intra-test repair assumptions
should be made based on the application.  In many cases repairs should be
treated as somewhere between "good as new" and "bad as old".  This requires more
complex modeling that is beyond the scope of this paper.

It should  also be noted that we are currently indexing both $\rho$ and
$\gamma$, only by $j$ and not $i$, in other words, we are assuming a single
shape and between phase adjustment parameter for each failure mode across
vehicles.  All of these parameters could also be indexed by $i$ and modeled
hierarchical or with some combination of both.  This is something we will omit
for this paper but hope to explore in the future.

\subsubsection{JLTV Reliability}
We have discussed different models structures and distributional assumptions
that accompany them.  Using McMC we fit each of these models to the JLTV
dataset.\footnote{The likelihoods and sampling distributions are available in the
appendix.} Then we use the posterior distributions of the systems parameters to
estimate reliability-related quantities of interest for each of the eight
vehicle types.  We are able to look at a number of different statistics related
to reliability at both the component and system level.  In this study, one
quantity of interest is expected miles to failure(EMTF).  In figure 1 we have box
plots and summary statistics from the posterior distributions of the expected
miles to failure for one of the vehicle types for each of the three phases,
first using the exponential model and second using the more general Weibull
model.

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
      \includegraphics[width=9cm, height=7cm]{Boxplots}
  % \caption{Comparing EMTF for Different Models}
  %\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \center
  \begin{tabular}{|c|c|c|c|c|}
  \multicolumn{5}{c}{\textbf{Summary Statistics}} \\
  \cline{1-5}
  Model & Phase & Mean & 90\% CI Low & 90\% CI Up \\
  \hline
  Expo & P1   & 129.98   & 110.22 &  152.23 \\
  Expo & P2   & 98.44  & 89.00 &  108.38  \\
  Expo & P3   & 135.89   & 117.78 &  155.45 \\
  Weibull & P1   & 169.96  & 116.95 & 236.16 \\
  Weibull & P2   & 135.24   & 104.89 & 167.48 \\
  Weibull & P3   & 175.51   & 138.87 & 214.23 \\
  \hline
  \end{tabular}
  %\label{fig:sub2}
\end{subfigure}
\caption{Comparing EMTF for Different Models}
\label{fig:test}
\end{figure}

You can see the posterior EMTF distributions from the Weibull model have more
spread than the exponential.  This is generally expected, given the Weibull
model is estimating two model parameters to the exponentials one, but what is
concerning is that the center of the distributions is also quite different
between the two models.  The Weibull EMTF posterior means are consistently
larger than the exponentials.  We saw this across all eight vehicle types.  This
was the first indication that the exponential model may not be a good fit to the
data.

\subsubsection{Model Diagnostics}
As seen in the last section with the JLTV data, the decision of which model to
use can have a drastic impact on reliability assessment.  We will now look at a
few  goodness-of-fit methods that can be used to help in this decision.  The
first model selection question we will explore is the parametric form,
exponential versus Weibull.  This an example of the classic statistical modeling
the trade-off between fit and interpretability.  Because the Weibull is a more
flexible model it will always, in a sense, fit the data better, but this comes
at a price.  The exponentials convenient form makes both computation and
interpretation straightforward.  When the Weibull's shape parameter is
introduced this advantage is lost.  Thus, when the overall fit is close to the
same between the exponential and the Weibull we will default to using the
exponential.

The first check we used in decide between the exponential and Weibull models is
to fit the Weibull model and look at the posterior distributions of the shape
parameters and determine if one is a reasonable value.  Looking at the plot in
figure 2 from the Weibull model fit with the JLTV data, we see that one is
not a reasonable value for any of the failure modes.  This is another clue
that the exponential model is not be a good fit to this data.

\begin{figure}[h]
  \centering
      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
  \caption{Posterior Plots of Weibull Shape Parameter}
\end{figure}

Now a more formal diagnostic tool, the Deviance information criterion (DIC)
~\cite{ref4}. This is a popular method for comparing the goodness of fit of
multiple models. The DIC method includes a penalty term that grows with the
numbers of unknown parameters in the model.  The DIC value is a unit-less
measure with lower values indicating a better fit to the data.  In the table
below we show the DIC results for the different distribution and structure
combinations, we considered with the JLTV dataset.

% need to recheck these numbers %
\begin{table}[h]
\centering
\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Common Rate Model                     & 21,264.19             \\
              & Hierarchical Rate Model               & 21,244.47             \\
Weibull       & Common Rate Model                     & 20,658.25             \\
              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
\hline
\end{tabular}
\caption{JLTV DIC Results}
\label{table:ta}
\end{table}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, fullpage, bbm}
\usepackage{array}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{color}
%\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

@@

%AGW: I just changed the margins and spacing to
%make things easier to proofread. Uncomment the following and
%comment out the doublespacing command below.
% DON'T change margins - should be 1 inch all around.
%\addtolength{\oddsidemargin}{-.5in}%
%\addtolength{\evensidemargin}{-.5in}%
%\addtolength{\textwidth}{1in}%
%\addtolength{\textheight}{-.3in}%
%\addtolength{\topmargin}{-.8in}%

@@

\author{James F.\ Gilman\\North Carolina State University\\Raleigh, NC\\\texttt{jfgilman@ncsu.edu} \and
Kassandra M.\ Fronczyk\\Lawrence Livermore National Laboratory\\Livermore, CA\\\texttt{fronczyk1@llnl.gov} \and
Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu}}
\maketitle} \fi

@@

\begin{abstract}
    We propose a Bayesian hierarchical model to assess the reliability of a family of vehicles, based on the development of the Joint
    Light Tactical Vehicle (JLTV). The proposed
    model effectively combines information across three phases of testing and
    across common vehicle components. The analysis yields estimates of failure
    rates for specific failure modes and vehicles as well as an overall estimate
    of the failure rate for the family of vehicles. We are also able to obtain
    estimates of how well vehicle modifications between test phases improve
    failure rates. In addition to using all data to improve on current
    assessments of reliability and reliability growth, we illustrate how to
    leverage the information learned from the three phases to determine
    appropriate specifications for subsequent testing that will demonstrate if
    the reliability meets a given reliability threshold.
\end{abstract}

@@

\newpage
\doublespacing
\section{Introduction}
Reliability is a high priority in the testing of defense systems. A common
metric is {\em reliability growth}, which tracks the change, and ideally
improvement, in the reliability of a system as it moves through testing phases
and undergoes periodic corrective actions. Ideally, plans for future test events
should be based on what has been observed in previous testing.

In this paper, we propose models for combining information across multiple test phases with
the objective of planning a future test. When combining information, there is no
omnibus solution. Rather, models need to be carefully considered and evaluated
to ensure that they accurately reflect the data and the underlying physical
processes. Our analysis is motivated by the reliability assessment of the Joint Light
Tactical Vehicle (JLTV), which is a family of vehicles designed to replace
one-third of the legacy high-mobility multipurpose wheeled vehicle (Humvee)
fleet. There are four unique types of vehicles, and within types there are many
possible variants. The primary mission of the family of vehicles is to provide
ground mobility that is deployable worldwide and capable of operating across the
range of military roles including combat, sustainment, police action,
peacekeeping, and security patrol, in all weather and terrain conditions.

The JLTV was evaluated using multiple test events as it was developed.
Engineering and Manufacturing Development (EMD) included three phases of
testing, where fixes occurred only during a set Corrective Action Period (CAP)
between each phase. For every vehicle, each failure encountered during testing
was recorded and attributed to a specific failure mode.  Since fixes were
delayed to CAPs, analysis generally shows a distinct jump in the system
reliability between test phases.

@@

\section{Data}
Eight vehicle prototypes were used for reliability, availability, and maintainability (RAM) testing of the JLTV. There were four two-seat utility vehicles,
two four-seat general purpose vehicles, a two-seat heavy guns carrier, and a
two-seat close combat weapons carrier. The close combat weapons carrier, one
general purpose, and two utility vehicles were tested in Aberdeen, Maryland, and the heavy weapons carrier, one general purpose, and two utility vehicles
were tested in Yuma, Arizona. When comparing the test sites, the Maryland test site is much colder in the winter months but the terrain is not as harsh; in Arizona, it is warmer but with more challenging terrain. Using two test sites allows for the system to be tested under a broader range of environmental conditions.
The vehicles were driven roughly 3000 to 5000 miles in Phase 1, between
4500 and 7500 miles in Phase 2, and between 5000 and 6700 miles in Phase
3.\footnote{The exact mileage has been altered to protect proprietary information. \textcolor{red}{Any other changes to the data that we should describe? I think things were perhaps rescaled, constants added, etc. Let's be sure this isn't a JLTV assessment, but based on the JLTV assessment.}}

There are many similarities between vehicle types; in fact, the most dissimilar
vehicles have over 80\% common parts. Consequently, some failure modes, such as
brakes and radios, will be common to all eight vehicles. Other failure modes
will be related, but not identical, as with hydraulics, frame, and body. There are 1412 observed failures attributed to 26 failure modes recorded across
all eight vehicles and all three test phases. In any given phase of test, every
vehicle is not guaranteed to have a failure of all 26 failure modes, and each
test phase does not necessarily end with a failure. Therefore, we have 624 right
censored observations, accounting for miles driven without observed failures.

\section{Methodology}
A standard reliability analysis employed by the Department of Defense (DoD) test
community considers each test phase independently and uses the exponential
distribution to model the miles between failure for the system ~\cite{ref1}. For many situations, including our example, this
traditional analysis is overly simplistic, relying on incorrect modeling assumptions and ignoring valuable information learned about the individual vehicles and their failure modes.

We propose an alternative approach using a Bayesian hierarchical
model.  The methodology section is organized as follows.  In Section~\ref{modrel}, we introduce a general structure that models the relationships in the
data across all test phases, while accounting for CAPs, and incorporates known
similarities between vehicle failure modes.  Next, we will consider different
distributional assumptions and their implications.  Using the JLTV case study we
will illustrate the process of model selection using three different diagnostic
checks.  In Section~\ref{atp} we discuss methods of designing next stage test plans.
First we outline the traditional approaches, then we propose a Bayesian
approach that allows the practitioner to incorporating the models developed from
Section~\ref{modrel} with the hopes of reducing testing resources required while minimizing producer and consumer risks.

\subsection{Modeling Reliability}\label{modrel}
In this reliability setting, we are analyzing time to failure data measured in
miles for a multiple component system with the primary objective of
assessing the system failure rate and predicting future failure counts.
The most common models used in this kind of failure rate analysis are lifetime
distributions, and the most common for failure count analysis is the
\emph{Poisson process} family of counting models.

\subsubsection{Model Structure}
For each phase of testing we have failure mileage data for
a given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the censored
observation at the end the testing phase. In each phase of testing, we assume
the vehicle miles between failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a
lifetime distribution, $f(\cdot)$, with an unknown set of parameters that include
a rate parameter.  For the first phase of testing, the rate parameter for vehicle $i$ and
failure mode $j$ will be denoted as $\lambda_{ij}$.  For the next stage, we use the same $\lambda_{ij}$ but add a multiplicative correction parameter
$\rho_{j}^{P2}$ that represents the change in this rate due to the CAP.  This
procedure is then repeated for each subsequent stage.  The correction parameter
will be discussed more in the next section, but the general model is:
\begin{align*}
\text{Phase 1: }&y_{ijk}\mid\lambda_{ij}\sim f(\cdot) \\
\text{Phase 2: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\sim f(\cdot) \\
\text{Phase 3: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\rho_{j}^{P3}\sim f(\cdot) \\
\quad i = 1,2,...,v \quad &j=1,2,...,s \quad k=1,2,...,n_{ij}
\end{align*}
where $v$ represents the number of vehicles, $s$ is the number of failure modes,
and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$.  \textcolor{blue}{The number of vehicles $v$ and number of failure modes $s$ are the same across each of the three phases.}

For the model we assume a prior distribution on the failure rate parameter
$\lambda_{ij}$.  This distribution depends on whether failure mode $j$ is
considered to be common across vehicles or related but not identical.  If
failure mode $j$ is considered common across vehicles, we will assume there is a
single failure rate $\lambda_j$ that is shared by all eight vehicles with a
prior distribution that has positive support.  In the case study, we will use a
non-informative gamma distribution.  For failure modes that are considered
related across vehicles, but that are not expected to be exactly the same, we place a
prior distribution on the collection of $\lambda_{ij}$; in other words, we
assume each of the vehicles has a distinct failure rate for failure mode $j$ but
they arise from a common distribution.  This is the common Bayesian hierarchical
modeling structure, where we then place  hyperprior distributions on the shared
distribution's parameters.  In the case study, we use a gamma distribution with
non-informative hyperpriors for all related failure modes.  Many times in
practice  it is difficult to know ahead of time if individual components should
be modeled  as common or related.  In the case study, we fit models for each
component with both model structures and used diagnostic tools  that are
discussed in a later section to make our final decision.

\subsubsection{Fix Effectiveness}
After the first CAP, the second test phase begins with the repaired vehicles. To capture
these repairs, the PM2 reliability growth model \cite{ref2} is often used.
This model explicitly captures testing phases, choices about which failure modes
to correct, and the potential of not completely eliminating a failure upon
repair. One of the features of PM2 is that many parameters of potential
interest, such as the Fix Effectiveness Factor (FEF), which measures how much
repairs improve failure rates, are typically fixed, as PM2 is often used as a planning model. A common value for FEF is
0.70. We follow the premise of this type of model, but allow a more flexible and
data-driven result.

One common assumption in reliability growth modeling is nondecreasing
failure rates: either the fixes were effective or had no effect, but did
not degrade the reliability of the family of vehicles.  This should generally be the case, but
because we are dealing with complex systems and testing conditions are rarely
completely consistent, we will sometimes see decreases in failure rates after repairs are made.  Thus we choose a prior distribution for the
FEF parameter $\rho_{j}^{P2}$ that has positive support.  If
$\rho_{j}^{P2}$ is less than one, this represents an improvement in reliability.
The same approach is applied to $\rho_{j}^{P3}$ for the correction period
between phases two and three.  With this structure we can use the posterior
distributions of the correction parameters to make inference on the effectiveness
of the repairs and the joint posterior distributions to evaluate the overall system reliability within each phase.

\subsubsection{Distributional Assumption}
The next modeling choice that must be made is selecting an appropriate
probability model. This includes a selecting a sampling distribution for the data
and prior distributions for each parameter on which the sampling distribution
depends. Some common distributional choices for lifetime data are exponential, Weibull, lognormal, gamma, inverse
Gaussian, and normal failure time models.  Because all of these distributions
have a rate parameter (sometimes called a scale parameter, which is the reciprocal of the rate parameter) they can be applied in
the proposed modeling structure. We focus on the
exponential and Weibull distributions, which are commonly used for reliability.

The exponential model has probability density function
\begin{equation*}
    f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}y_{ijk})
\end{equation*}

This is by far the most common parametric distribution used in reliability
modeling because of its desirable mathematical properties and straightforward interpretations.  One convenient property, because we are assuming
independence between failure modes, is that the overall system failures also follow
an exponential distribution with a system failure rate $\lambda_S =
\sum_{j}\lambda_{j}$.  A second, potentially less attractive property, is that the hazard rate is constant over miles.  For the case study, this implies that a given
component is equally likely to fail in the first mile of testing as it is in the thousandth.  This may be reasonable for some components, but in many settings we observe either a decreasing hazard rate, where failures are likely to
occur early in testing but less likely as the test goes on, or an increasing hazard rate, where we see the system wear down as the test progresses.

Despite its common use, the assumption of a constant hazard rate over time is rarely justifiable. The issues that arise when the modeling assumptions for the exponential distribution are violated are well-documented ~\cite{ref3}. Therefore, we will also consider more flexible distributions when analyzing the data.  In our analysis of the case study, we also fit the same hierarchical model structure using the Weibull as our
lifetime distribution, $f(\cdot)$. We assume that the failure mileage $t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$ distribution with scale
parameter $\lambda$ and shape parameter $\gamma$, with probability density
function,
\begin{equation*}
    f(t_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
    t_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} t_{ijk}^{\gamma_{i}}).
\end{equation*}
The exponential is a special case of the Weibull, when $\gamma = 1$.

\textcolor{blue}{When a failure occurs during a testing phase the mileage is recorded and the system is restored to full operation, often by repairing or replacing a component.  One must consider how these changes will effect the system reliability moving forward.  In repairable system literature two common modeling assumptions are the extreme cases ``good as new" or ``bad as old".  ``Good as new" assumes that a repaired component has returned to a brand-new state or in our case the the mileage is set to zero.  On the other hand, ``bad as old" assumes the component has returned to the state it was at before the failure occurred.  You will notice for the Weibull we assuming ``bad as old" intra-test repairs by modeling the actual failure mileage $t_{ijk}$ instead of the miles between failures $y_{ijk}$.}  We could have continued with the miles between failures and assumed "good as new" repairs, but "bad as old" modeling will be more
convenient for developing assurance test plans in later sections.  This distinction is important in the Weibull case because the failure rate is not constant in time. In practice the decision on intra-test repair assumptions should be made based on the application.  In many cases repairs should be treated as somewhere between "good as new" and "bad as old".  This requires more complex modeling that is beyond the scope of this paper.

We index both $\rho$ and
$\gamma$ only by $j$ and not $i$. In other words, we are assuming a single
shape and between phase adjustment parameter for each failure mode across
vehicles.  All of these parameters could also be indexed by $i$ and modeled
hierarchical or with some combination of both. \textcolor{blue}{When failure modes do not occur within the testing period, resulting in a single censored observation, this can lead to convergence issues.  In the case study, we found 6 of the 26 failure modes had less than 10 observed (non-censored) failures across all 3 phase and 8 vehicle types.  These failure modes were attributed to system components such as the engine and armor.  To improve convergence we have binned these rare failure modes into a single "other" failure mode.  This is also useful for future testing in the case of observing failures not originally accounted for. }

\subsubsection{Model Diagnostics}
The decision about which model to
use can have a substantial impact on reliability assessment.  We consider a
few  goodness-of-fit techniques that can be used to help with this decision for Bayesian reliability models.  The
first model selection question we consider is the parametric form,
exponential versus Weibull.  This an example of the classic statistical modeling
the trade-off between fit and interpretability.  Because the Weibull is a more
flexible model, containing the exponential as a special case, it will always fit the data at least as well as the exponential.  The exponential distribution's convenient form makes both computation and
interpretation straightforward.  However, when the Weibull distribution's shape parameter is
introduced this advantage is lost.

The first diagnostic we use to decide between the exponential and Weibull models is
to fit the Weibull model and look at the posterior distributions of the shape
parameters to determine whether their support contains 1. From Figure~\ref{Shape}, which shows the Weibull model fits for the case study for each failure mode, we see that 1 is not a reasonable value for any of the failure modes, which suggests that the exponential model may not fit this data well.

\begin{figure}[h]
  \centering
      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
  \caption{Posterior Plots of Weibull Shape Parameter}
  \label{Shape}
\end{figure}

We also consider a more formal diagnostic tool, the Deviance information criterion (DIC)
~\cite{ref4}. This is a popular method for comparing the goodness of fit of
multiple models. The DIC method includes a penalty term that grows with the
numbers of unknown parameters in the model.  The DIC value is a unitless measure with smaller values indicating a better fit to the data.  Table~\ref{table:ta1} shows the DIC results for the different distribution and structure
combinations, we considered for the case study. The results show that the hierarchical Weibull model fits the data
much better than the exponential or common rate models.

% need to recheck these numbers %
\begin{table}[h]
\centering
\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Common Rate Model                     & 21,264.19             \\
              & Hierarchical Rate Model               & 21,244.47             \\
Weibull       & Common Rate Model                     & 20,658.25             \\
              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
\hline
\end{tabular}
\caption{JLTV DIC Results}
\label{table:ta1}
\end{table}

In general, information criteria
comparisons do not tell us if the model is truly a good representation of the
underlying process -- they only compare models. The final model diagnostics method we present is called
posterior predictive checking ~\cite{ref5}.  We start with important
features of the data that we would expect to see if the experiment was repeated.
These are usually provided by practitioner with knowledge about the random
process being studied. In the case study, \textcolor{blue}{one feature of interest is the count of miles between failure observations less than 140 miles, for a given vehicle and phase.}

%\textcolor{blue}{for each phase, $\sum \mathbbm{1} [y_{ijk} < 140]$.}

We used the final \textcolor{blue}{exponential and Weibull models with the lowest DIC} to simulate 5,000 new datasets for vehicles tested
over the same number of miles for each of the three phases. We plot the resulting distributions for each of the 8 vehicles for all 3 phases. Figure~\ref{fig:test} shows two examples of the boxplots produced, one from the exponential model
(left) and one from the Weibull model (right), with the dashed line showing
where the value from the observed dataset fell. If the model fits reasonably well, we expect to see the value from the observed data falling within the support of the simulated data. This suggests that the Weibul model fits the case study data better than the exponential data.

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPExpo}
  %\caption{}
  %\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPWeibull}
  %\caption{}
  %\label{fig:sub2}
\end{subfigure}
\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
\label{fig:test}
\end{figure}
